\emph{icepack}: a new glacier flow modeling package in Python, version 1.0

### 2021-01-12 icepack.tex
Use short commit hashes

\codedataavailability{
All code used in this repository is free and open source and all data sets used in the demonstrations are publicly available.
The icepack source repository is at https://github.com/icepack/icepack.
Icepack is released under the GPLv3 license.
The git commit hash of the version of the code used for this publication is b78b0ee571590cf5af242101c159154c6872b7b9, see also the Zenodo release at https://doi.org/10.5281/zenodo.1205640.
The icepack documentation and user manual is hosted at https://icepack.github.io.
The source code for the demonstrations used in this paper is hosted at https://github.com/icepack/icepack-paper, commit hash 4db3dc281e83b4304751ded3b77f166942b0efc6.
The demonstrations used glacier outlines that were hand-digitized from satellite imagery in order to generate the model domains.
These outlines are kept in version control and hosted at https://github.com/icepack/glacier-meshes and the git commit hash for the version used in this publication is c98a8b7536b1891611566257d944e5ea024f2cdf.
Additional observational data are hosted at the US National Snow and Ice Data Center (https://www.nsidc.org).
}

>>>>

\codedataavailability{
All code used in this repository is free and open source and all data sets used in the demonstrations are publicly available.
The icepack source repository is at https://github.com/icepack/icepack.
Icepack is released under the GPLv3 license.
The git commit hash of the version of the code used for this publication is b78b0ee5, see also the Zenodo release at https://doi.org/10.5281/zenodo.1205640.
The icepack documentation and user manual is hosted at https://icepack.github.io.
The source code for the demonstrations used in this paper is hosted at https://github.com/icepack/icepack-paper, commit hash 4db3dc28.
The demonstrations used glacier outlines that were hand-digitized from satellite imagery in order to generate the model domains.
These outlines are kept in version control and hosted at https://github.com/icepack/glacier-meshes and the git commit hash for the version used in this publication is c98a8b75.
Additional observational data are hosted at the US National Snow and Ice Data Center (https://www.nsidc.org).
}
